%%% Pixel Development

The first step of the visualization required that the United States
be broken up into pixels so that trips could be easily identified
and tracked. Our analysis considers the 48 contiguous states,
which together span around 3.8 million square miles. Each square
pixel spans an area of .25 miles, implying that around 12 million 
pixels are needed to uniquely map the entire country. 
The center of the National grid is at 37\textdegree  N Latitude, 
-97.50\textdegree W Longitude, placing the grid's centroid
close to the geographic center of the continental US along the time meridian.


\section{Pixel Structure and Algorithm Method}
The primary motivation for creating a pixelated grid is 
to establish a simple method to track, store and retrieve 
trips within the pixel. Thus each pixel object 
must contain a unique id, an (i,j) coordinate, and
the latitude and longitude of its four corners and its centroid.  

\subsection{Geometric Analysis}
In order to algorithmically create a pixelated grid, a methodology 
of mapping latitude and longitude to (i,j) coordinates was established. 
Given that along a Meridian each degree of latitude traverses approximately 69.174 miles and
that along a Parallel each degree of longitude traverses approximately $69.174\cdot \cos(Latitude\textdegree)$
one can map any latitude and longitude coordinate to an (i,j) pixel. To determine the set of (lon, lat) coordinates
within a pixel, the angular height and width of each pixel as calculated. The Y-height of a pixel is 0.00722814 degrees Latitude and 
the X-width of a pixel is 0.00944344 degrees Latitude. 
Each (i,j) Pixel thus includes all points within:
\begin{align}
	&\textsl{YHeight} = 0.00722814  \:\: | \: \: \textsl{CenterLat} = 97.5\textdegree \: \: | \: \: \textsl{CenterLon} = 37.0\textdegree
\end{align}
\begin{align}
	\frac{CenterLat + YHeight \cdot i}{\cos(CenterLon + YHeight \cdot j)} \leq &\textsl{Longitude}  
	< \frac{CenterLat + YHeight \cdot (i+1)}{\cos(CenterLon + YHeight\cdot (j+1)} \\
	CenterLat + YHeight\cdot j \leq & \textsl{Latitude} < CenterLat + YHeight \cdot (j+1)
\end{align}

The inverse of the equation above was used to map (lon, lat) coordinates to pixel coordinates and 
was imperative in constraining our algorithm to the US. 

\begin{align}
 \textsl{xPixel} = & i = floor(138.348 \cdot \text.sl{longitude + CenterLat} \cdot \cos(\textsl{latitude})) \\
  \textsl{yPixel} = & j = floor(138.348 \cdot \text.sl{latitude - CenterLon})
\end{align}

Where floor casts the decimal result as an integer, rounded down, and 138.348 is a correcting constant. 
\subsection{Methodoloy}

The southwest and northeast corner of the US provided the initial and final (lon, lat) 
coordinates of our grid. The initial point (southwest corner) has a longitude of  -120.5\textdegree and a latitude of -63.5\textdegree. The final point (northeast corner) has a longitude of -63.5\textdegree and a latitude of 48.9\textdegree. Using equation 2.4 and 2.5, the initial and final (i,j) coordinates corresponding to the corners of the nation were found and used as starting and breaking conditions during pixel construction. Then, running through a double for loop indexed by i and j, each (i,j) pair was sent to a Pixel class for creation and then added to a hashtable. The Pixel class takes an (i,j) coordinate in its constructor and using the equations in 2.1.1 determines the longitude and latitude of its four corners and centroid. Furthermore, in order to prevent collisions within the hashtable, each pixel creates a unique id by using its (i,j) coordinates as the input for the Cantor pairing function, which uniquely encodes two natural numbers into a single natural number. Since the Cantor pairing function only holds for positive numbers, i and j are offset by the absolute value of the initial (i,j) point.
\begin{multline*}
\label{eq: Cantor Function}
\tag{Cantor Function}
f_{ij} = (1/2) \cdot (i + |\textsl(InitialX + Initial Y)| + j ) \cdot (i + |\textsl(InitialX + Initial Y)| + j + 1) + j + |\textsl(InitialY)| 
\end{multline*}
A sketch of the initialization loop is shown below.
\begin{verbatim}
        for i in range(iStart, iEnd): 
          	for j in range(jStart, jEnd):
                    Pixel = createPixel(i,j)
                    Pixels.add(Pixel.key(), Pixel)
\end{verbatim}

\subsection{Additional Structure: The Use of Subsections}
\label{sec:structure} We are in a subsection now (two levels down
from a Chapter). When we refer to $X.Y.Z$, we mean Chapter $X$,
Section $Y$, and subsection $Z$. We declare a Chapter by the command
\verb|\chapter{|\emph{title of Chapter}\verb|}|, a Section by
\verb|\section{|\emph{title of Section}\verb|}|, and so on.

The nice thing about \LaTeX{} is that it takes care of the chapter,
section, and subsection numbering automatically. If I were to add
another subsection before this one the subsection number would
change (increment by one). This section is \ref{sec:structure} and I
referred to it using the command \verb|\ref{|\emph{label of this
section}\verb|}|. I inserted a label right after the
\verb|\subsection| declaration by typing \verb|\label{|\emph{label
of this section}\verb|}|.

\subsubsection{A subsubsection}\label{subsub} Just for fun! Notice
that no number is alloted for such a low level environment but it
sometimes useful.

\subsection{Another Subsection}
And so on\ldots.

\section{Mathematical Symbols}
Let $X=\{X_n, n\in \N\}$ be a Markov chain with state space
$\mathcal{D}$. Throughout this thesis, we use the notation
\begin{equation}
p_{ij} := \P\{X_{n+1} = j \mid X_n = i\}, \quad i,j \in \mathcal{D}
\label{pij}
\end{equation}
for the transition probabilities of the Markov chain $X$.
Furthermore, we denote by $P$ the transition matrix, $P =
[p_{ij}]_{i,j\in\mathcal{D}}$.

When we wrote \eqref{pij} we implicitly assumed that the Markov
chain $X$ is time-homogeneous.

Let us also define $Y$,
\begin{equation*}
Y = (Y_n)_{n = 0,1,2,\ldots}
\end{equation*}
to be another process. Notice that the second equation does not take
a number on the right---this is the use of \verb|\begin{equation*}|
environment.

Notice that the all the math characters, $X$, $\mathcal{D}$, and
others such as $\alpha, \beta, \gamma$ are part of the text in
\LaTeX{}. On the contrary, Word includes such characters as foreign
objects (usually images), which increases the size of the document
file, sometimes makes them disappear, but most importantly are not
as aesthetically pleasing as the resulting characters here.

\section{Citing and Bibliography}
When working with large documents you need an easy way to cite your
references without having to go back to your list all the time to
remember the names of the authors and the year of publication. Even
more importantly, you need to have all your references listed in the
end of the document in alphabetical order. Of course, they all need
to be syntactically the same so that alone makes the manual entry of
references a big pain. Thankfully, \LaTeX{} takes care of that in a
very easy and elegant way, using \BibTeX.

I cite here a few books, papers, and technical reports, and please
go to page \pageref{bib} to see the resulting bibliography.

According to the books by \cite{C75}, \cite{BR02}, and \cite{MR97}
and the articles by \cite{DG01}, \cite{BBM05}, and \cite{CFPS04} we
conclude absolutely nothing. However, in his report, \cite{A04}
claims that otherwise. All these citations were entered by \verb|\cite{|\emph{citation label}\verb|}|.
 
Notice the different citation style that follows: it is parenthetical, and observe that only one pair of parentheses is required \cite[see Theorem 5.2][pg. 32]{AMM05}. This citation is entered by typing \verb|\cite[see Theorem 5.2][pg. 32]{AMM05}| in the \verb|.tex| file. (Here, the citation label corresponding to \cite{AMM05} is obviously \verb|AMM05|.)


The citations are included in the file \verb|refs.bib| under the
folder \verb|Bibliography|. You can modify it and make your own
references. I highly recommend using \emph{JabRef} for managing your bibliography entries, because it makes it a piece of cake to do a lot of \emph{dirty} work. \emph{JabRef} is free and it works as a Java Application.

Also notice that \LaTeX{}, by default, includes in the Bibliography section only the references you actually cited throughout the text. If you want a source to appear in the Bibliography section without actually citing it anywhere in your text use the command \verb|\nocite{|\emph{citation label}\verb|}|. For example here I type \verb|\nocite{B95}| \nocite{B95} and you see no citation appear---however look at the fourth entry of the Bibliography. That cited book does not appear anywhere in this thesis, other than the Bibliography.

\section{Referencing Figures and Tables}
The very informative Figure~\ref{fig:dens} is on page~\pageref{fig:dens}. Both of these numbers were automatically generated---which is great when you add a new figure before the one you just inserted, because the numbering changes automatically for you. Use \verb|\ref{fig:dens}| for the figure number and \verb|\pageref{fig:dens}| for the page number where the figure is located. Here, \verb|fig:dens| was the label of the figure (see actual \verb|.tex| file for more information). Remember that \LaTeX{} does not work like Word---the figures and tables are \textbf{not} always placed exactly where you want them, so avoid writing ``according to the figure below\ldots,'' and prefer writing ``according to Figure~[\emph{figure number}]\ldots,'' instead. The same things go unchanged for tables. Notice that when I talk about figures and tables in general, I do not need to capitalize them, however if I talk specifically about Figure~\ref{fig:dens} and Table~\ref{tab:cdo}, I'd better respect them and capitalize the `f' and the `t.'

Since we're at it, notice that the quotes `, ', ``, '' are not inserted like in Word. For ` you need to use the \verb|`| key that is located above the \verb|Tab| button. For ' you just press the \verb|'| key, exactly to the left of the \verb|Enter| key. For double quotes just double the appropriate single quotes without leaving any space.
